### 2025-01-03 README.Rmd
README formatting
add new functionality to README

* `load_embeddings()` loads pretrained [GloVe](https://nlp.stanford.edu/projects/glove/), [word2vec](https://code.google.com/archive/p/word2vec/), [ConceptNet Numberbatch](https://github.com/commonsense/conceptnet-numberbatch), and [fastText](https://fasttext.cc) word embedding models from Internet sources or from your working directory
* `embed_tokens()` returns the embedding for each token in a set of texts
* `embed_docs()` generates text embeddings for a set of documents
* `get_sims()` calculates row-wise similarity metrics between a set of embeddings and a given reference
* `average_embedding()` calculates the (weighted) average of multiple embeddings
* `reduce_dimensionality()` reduces the dimensionality of embeddings
* `normalize()` and `normalize_rows()` normalize embeddings to the unit hypersphere
* and more...

@@

```{r}
valence_df_2d <- valence_embeddings_df |> 
	reduce_dimensionality(dim_1:dim_25, 2)
valence_df_2d
```
`reduce_dimensionality()` can also be used to apply the same rotation other embeddings not used to find the principle components.

@@

>>>>

* `load_embeddings()` loads pretrained [GloVe](https://nlp.stanford.edu/projects/glove/), [word2vec](https://code.google.com/archive/p/word2vec/), [ConceptNet Numberbatch](https://github.com/commonsense/conceptnet-numberbatch), and [fastText](https://fasttext.cc) word embedding models from Internet sources or from your working directory
* `embed_tokens()` returns the embedding for each token in a set of texts
* `embed_docs()` generates text embeddings for a set of documents
* `get_sims()` calculates row-wise similarity metrics between a set of embeddings and a given reference
* `average_embedding()` calculates the (weighted) average of multiple embeddings
* `reduce_dimensionality()` reduces the dimensionality of embeddings
* `align_embeddings()` rotates the embeddings from one model so that they can be compared with those from another
* `normalize()` and `normalize_rows()` normalize embeddings to the unit hypersphere
* and more...

@@

```{r}
valence_df_2d <- valence_embeddings_df |> 
	reduce_dimensionality(dim_1:dim_25, 2)
valence_df_2d
```
`reduce_dimensionality()` can also be used to apply the same rotation to other embeddings not used to find the principle components.

@@

#### Align and Compare Embeddings Models

Aligning separately trained embeddings can be useful for tracking semantic change over time or semantic differences between training datasets. It can also be useful for comparing texts across languages. `align_embeddings(x, y)` rotates the embeddings in `x` (and changes their dimensionality if necessary) so that they can be compared with those in `y`. Optionally, `matching` can be used to specify one-to-one matching between  embeddings in the two models (e.g. a bilingual dictionary).

Once aligned, groups of embeddings can be compared using `total_dist()` or `average_sim()`. These can be used to quantify the overall distance or similarity between two parallel embedding spaces.
